---
title: "Fort Bragg Weather"
author: "SL"
date: "August 12, 2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(sf)
library(tidyverse)
library(viridis)
library(rvest)
library(rgeos)
library(lwgeom)
library(purrr)
library(purrrlyr)
library(tmap)
library(knitr)
library(kableExtra)
library(rnaturalearth)
library(rnaturalearthdata)
library(ncdf4)
library(devtools)
library(raster)
library(ncdump)
library(lubridate)
library(flipTime)
library(fuzzyjoin)
library(RNetCDF)
library(tidync)
library(furrr)
library(humidity)
library(HeatStress) #devtools::install_github("anacv/HeatStress")
library(weathermetrics)
library(wbgt)  #devtools::install_github("mdljts/wbgt")

```

## Load installation shapefile
Accessed from: https://catalog.data.gov/dataset/military-installations-ranges-and-training-areas
Metadata updated date: January 18, 2017
```{r load_shapefile}
#Ref: http://strimas.com/r/tidy-sf/
bases <- st_read("installations_ranges/MIRTA_Boundaries.shp") %>% 
  janitor::clean_names()

```

## Select installation
```{r select_sf_dataframe, warning = FALSE}
## Create dataframe of active duty Army installations, including FSH (JBSA) and single Fort Benning row 

bragg_sf <-
  bases %>%
    filter(site_name == "Fort Bragg")

as_tibble(bragg_sf)
```

## Plot shapefile

```{r plot_selected_bases}

## Plot selected installations
bragg_sf %>% 
  ggplot() +
     geom_sf() +
     ggtitle("Fort Bragg, NC") +
                theme_bw() +
                theme(axis.text.x = element_text(size = rel(0.6)),
                      axis.text.y = element_text(size = rel(0.6))) 
```

## Load NLDAS grids
NLDAS grid shapefile from: https://ldas.gsfc.nasa.gov/sites/default/files/ldas/nldas/NLDAS_Grid_Reference.zip

```{r load_nldas_grid}

nldas_grid <- st_read("nldas_grids/NLDAS_Grid_Reference.shp") %>% 
  janitor::clean_names()

as_tibble(nldas_grid)

```


## NLDAS and Installation Grid Overlap and Weighted Averages

```{r nldas_intersection_indiv}

bragg_nldas <-
  st_intersection(bragg_sf, nldas_grid) %>% 
  mutate(area = sf::st_area(.),
         weight = area / sum(area))

bragg_intersects <-
  nldas_grid %>% filter(lengths(st_intersects(., bragg_sf)) > 0)

```

```{r grid_weights}
# Total Area
sum(bragg_nldas$area)
# Check sum of grid spatial area weights (should equal 1)
sum(bragg_nldas$weight)
# List intersected grid areas
st_area(bragg_nldas) 

bragg_nldas %>% 
  as_tibble() %>% 
  select(nldas_id, weight) %>%
  mutate(weight = as.vector(weight),
    percent = (weight / sum(weight)) * 100) %>% 
  knitr::kable()
```


```{r plot_nldas}
ggplot() + 
  ggtitle("Fort Bragg NLDAS grids") +
  geom_sf(data = bragg_intersects) +
  geom_sf(data = bragg_nldas) +
  geom_text(data = bragg_nldas, aes(x = centerx, y = centery, label =  formatC(weight, format = "f", digits = 3)) , size = 3, position = position_nudge(y = -0.02)) +
  geom_label(data = bragg_nldas, aes(x = centerx, y = centery, label = nldas_id), size = 3, fontface = "bold") +
  theme_bw()
```

## Full bounding box for installation
```{r bounding_box_indiv, eval=FALSE, warning = FALSE}
# Full bounding box of shapefile

st_bbox(bragg_sf) %>% 
  .[c("ymin", "xmin", "ymax", "xmax")]


st_as_sfc(st_bbox(bragg_sf))

```


# Select bounding box

Center coordinates from NLDAS grids x366y82 : x369y81

```{r}
select_bb_bragg <-
bragg_nldas %>% 
  filter(nldas_id %in% c("x366y82", "x369y81")) %>% 
  select(centerx, centery) %>% 
  as_tibble() %>% 
  mutate(ymin = centery[1],
         xmin = centerx[2],
         ymax = centery[2],
         xmax = centerx[1]) %>% 
  select(ymin:xmax) %>% slice(1)

select_bb_bragg

bragg_nldas %>% 
  as_tibble() %>% 
  select(nldas_id, weight) %>%
  slice(2:9) %>% 
  mutate(weight = as.vector(weight),
         mod_weight = weight / sum(weight),
         percent = (weight / sum(weight)) * 100) %>% 
  knitr::kable()
  

```


## Air Force Weather Stations (All)

```{r}
sar <-
  read.csv("D:/sar_weather/Lat_Long Coords for Army Garrisons.csv") %>% 
  janitor::clean_names()

sar_sf <-
  st_as_sf(sar, coords = c("lon", "lat")) %>% 
  st_set_crs(4326)

sar_sf

world <- ne_countries(scale = "medium", returnclass = "sf")

ggplot() +
  geom_sf(data = sar_sf)

ggplot() + 
  geom_sf(data = world) +
   geom_sf(data = sar_sf)

```

## AF weather station (select)
```{r}

bragg_sar <-
  sar_sf %>% 
    filter(name == "Fort Bragg")

```


```{r}
ggplot() + 
  ggtitle("Fort Bragg NLDAS grids") +
  geom_sf(data = bragg_intersects) +
  geom_sf(data = bragg_nldas) +
  geom_text(data = bragg_nldas, aes(x = centerx, y = centery, label =  formatC(weight, format = "f", digits = 3)) , size = 3, position = position_nudge(y = -0.02)) +
  geom_label(data = bragg_nldas, aes(x = centerx, y = centery, label = nldas_id), size = 3, fontface = "bold") +
  geom_rect(data = select_bb_bragg, 
            aes(xmin = xmin , xmax = xmax, ymin = ymin, ymax = ymax), color = "blue", fill = "transparent") +
  geom_sf(data = bragg_sar) +
  theme_bw()
```

# NLDAS-2 Data


## Open 1st NetCDF file to inspect variable names
```{r extract_variable_names}

file_list <- list.files(path = "D:/nldas", pattern = "^.*\\.(nc4|NC4|Nc4|Nc4)$")
head(file_list)

file_path <- paste0("D:/nldas/", file_list)
head(file_path)

file_name <- file_path[1]

# Open a connection to the first file in  list
nc1 <- ncdf4::nc_open(file_name)
tidync(file_name)

var_names <- attributes(nc1$var)$names
var_names

# Close the connection to the nc file
nc_close(nc1)
```

## Function to read ncdf4 files
- Filter by spatial bounding box coordinates
- Extract desired variables from grid/dimension and combine in dataframe

```{r read_ncdf_function}

as.data.frame(select_bb_bragg)

read_nc4 <- function(input_file) {
  
  nc4 <- tidync(input_file) %>%    
    hyper_filter(
      lat = between(lat, 35.0625, 35.1875 ),
      lon = between(lon, -79.3125, -78.9375)) 
  
    a <-
      nc4 %>% 
        activate("D0,D1,D2,D5") %>% 
        hyper_tibble() %>% 
        dplyr::select(lon, lat, TMP, SPFH)

    b <-
      nc4 %>% 
        activate("D0,D1,D3,D5") %>% 
        hyper_tibble() %>% 
        dplyr::select(-height_2, -time)

    c <- 
      nc4 %>% 
        activate("D0,D1,D5") %>% 
        hyper_tibble() %>% 
        dplyr::select(-DLWRF, -CONVfrac, -PEVAP, -APCP, -time)

    left_join(a, b, by = c("lat", "lon")) %>% 
    left_join(., c, by = c("lat", "lon")) %>% 
    mutate(date_time = 
           file_name %>% 
                stringr::str_extract("[1-2][0-9]{7}\\.[0-9]{2}[0]{2}") %>%
                stringr::str_replace("(\\d{4})(\\d{2})(\\d{2})(\\.)(\\d{2})(\\d{2})$", "\\1-\\2-\\3 \\5:\\6\\:00") %>% 
                  flipTime::AsDateTime(us.format = TRUE, time.zone = "UTC")) %>% 
    janitor::clean_names() 

}

```

## Map over function with each ncdf4 file

```{r map_over_ncdf_function}

plan(multiprocess)

ptm <- proc.time()
bragg_nldas_df <- furrr::future_map_dfr(file_path, read_nc4, .progress = TRUE) 
proc.time() - ptm

bragg_nldas_df

```


```


