---
title: "NLDAS Extract"
author: "SL"
date: "August 12, 2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(sf)
library(tidyverse)
library(viridis)
library(rvest)
library(rgeos)
library(lwgeom)
library(purrr)
library(purrrlyr)
library(tmap)
library(knitr)
library(kableExtra)
library(rnaturalearth)
library(rnaturalearthdata)
library(ncdf4)
library(devtools)
library(raster)
library(ncdump)
library(lubridate)
library(flipTime)
library(fuzzyjoin)
library(RNetCDF)
library(tidync)
library(furrr)
library(humidity)
library(HeatStress) #devtools::install_github("anacv/HeatStress")
library(weathermetrics)
library(wbgt)  #devtools::install_github("mdljts/wbgt")

```

## Load installation shapefile
Accessed from: https://catalog.data.gov/dataset/military-installations-ranges-and-training-areas
Metadata updated date: January 18, 2017
```{r load_shapefile}
#Ref: http://strimas.com/r/tidy-sf/
bases <- st_read("installations_ranges/MIRTA_Boundaries.shp") %>% 
  janitor::clean_names()

```

# NLDAS-2 Data

## Open 1st NetCDF file to inspect variable names

Full date range is from 1979 to present.

Select from 1990 to present. 
```{r extract_variable_names}

file_list <- list.files(path = "D:/nldas", pattern = "^.*\\.(nc4|NC4|Nc4|Nc4)$") %>% 
  as_tibble() %>% 
  mutate(date = value %>% 
           stringr::str_extract("[1-2][0-9]{7}") %>% lubridate::ymd(),
         hour = value %>% 
           stringr::str_extract("[1-2][0-9][0]{2}") %>% as.integer(),
         path = paste0("D:/nldas/", value)) %>% 
  dplyr::select(path, date, hour)
 
head(file_list)

```

## Function to read ncdf4 files
- Filter by spatial bounding box coordinates
- Extract desired variables from grid/dimension and combine in dataframe

```{r inputs}

site <- "bragg"

# Bounding box
lat1 <- 35.05
lat2 <- 35.22
lon1 <- -79.35
lon2 <- -78.93


```



```{r read_ncdf_function}

read_nc4 <- function(input_file) {
  
  nc4 <- tidync(input_file) %>%    
    hyper_filter(
      lat = between(lat, lat1, lat2),
      lon = between(lon, lon1, lon2)) 
  
    grid1 <-
      nc4 %>% 
        activate("D0,D1,D2,D5") %>% 
        hyper_tibble() %>% 
        dplyr::select(lon, lat, TMP, SPFH)

    grid2 <-
      nc4 %>% 
        activate("D0,D1,D3,D5") %>% 
        hyper_tibble() %>% 
        dplyr::select(UGRD, VGRD)

    grid4 <- 
      nc4 %>% 
        activate("D0,D1,D5") %>% 
        hyper_tibble() %>% 
        dplyr::select(PRES, DSWRF)

    bind_cols(grid1, grid2, grid4) %>% 
      
    bind_cols(grid1, grid2, grid4) %>% 
      mutate(date_time = 
              input_file %>% 
                stringr::str_extract("[1-2][0-9]{7}\\.[0-9]{2}[0]{2}") %>%
                stringr::str_replace("(\\d{4})(\\d{2})(\\d{2})(\\.)(\\d{2})(\\d{2})$", "\\1-\\2-\\3 \\5:\\6\\:00")) 
    
}






```

## Map over function with each ncdf4 file

Extract hourly variables for 

```{r map_over_ncdf_function}

num_years <- 1
num_obs <- num_years * 366 * 24
  
nldas_df <- data.frame(lon = rep(NA, num_obs), lat = rep(NA, num_obs), TMP = rep(NA, num_obs),
                             SPFH = rep(NA, num_obs),UGRD = rep(NA, num_obs),VGRD = rep(NA, num_obs),
                             PRES = rep(NA, num_obs),DSWRF = rep(NA, num_obs),date_time = rep(NA, num_obs))


year_range <- 1996:2019

plan(multiprocess)

ptm <- proc.time()

for (i in year_range)  {
 
  file_path <-  file_list %>% 
    filter(lubridate::year(date) == i) %>% 
      dplyr::select(path) %>% as_vector()
  
  nldas_df <- data.frame(lon = rep(NA, num_obs), lat = rep(NA, num_obs), TMP = rep(NA, num_obs),
                SPFH = rep(NA, num_obs),UGRD = rep(NA, num_obs),VGRD = rep(NA, num_obs),
                PRES = rep(NA, num_obs),DSWRF = rep(NA, num_obs),date_time = rep(NA, num_obs))
  
  nldas_df <- furrr::future_map_dfr(file_path, read_nc4, .id = NULL, .progress = TRUE)
  
  write.csv(nldas_df, paste0("D:/nldas_sites/", site, "_", i, ".csv"))
  
}            
proc.time() - ptm






plan(multiprocess)

ptm <- proc.time()
bragg_test <- furrr::future_map(file_path, read_nc4, .progress = TRUE) 
proc.time() - ptm



```


```


