---
title: "raster"
author: "SL"
date: "October 2, 2019"
output: html_document
---

This markdown extracts variables from NLDAS-2 netCDF files by converting .nc4 to raster and selecting by raster cell position. It includes a function to extract a single file and applies purrr:map2_dfc to map over each file and each defined variable.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(sf)
library(tidyverse)
library(viridis)
library(rvest)
library(rgeos)
library(rgdal)
library(lwgeom)
library(purrr)
library(purrrlyr)
library(tmap)
library(knitr)
library(kableExtra)
library(ncdf4)
library(devtools)
library(raster)
library(ncdump)
library(lubridate)
library(flipTime)
library(fuzzyjoin)
library(RNetCDF)
library(tidync)
library(furrr)
library(raster)
library(easyNCDF)
library(tmap)
library(rts)
library(tabularaster)
library(velox)
library(rgis)  # devtools::install_github("Pakillo/rgis")
library(parallel)
library(data.table)
library(compiler)
library(zoo)

```

## Load installation shapefile
Accessed from: https://catalog.data.gov/dataset/military-installations-ranges-and-training-areas
Metadata updated date: January 18, 2017


```{r load_shapefile}
#Ref: http://strimas.com/r/tidy-sf/
bases <- st_read("installations_ranges/MIRTA_Boundaries.shp") %>% 
  janitor::clean_names()

bases %>% 
 filter(component == "Army Active") 

army_select <-
  bases %>% 
    dplyr::filter(.$site_name %in% c("Fort Benning GA", "Fort Bragg","Fort Campbell",
                              "Fort Jackson", "Fort Polk", "Fort Hood",
                              "Fort Stewart", "Fort Leonard Wood", "Fort Riley",
                              "NTC and Fort Irwin", "Fort Bliss", "Fort Lewis",
                              "Fort Sill", "Fort Huachuca", "Fort Carson", "Fort Gordon",
                              "West Point Mil Reservation", "Fort Drum")) %>% 
    mutate(centroid = st_centroid(geometry),
           site_name = as.character(site_name)) %>% 
    dplyr::select(c("site_name", "centroid"))


```

# NLDAS-2 Data

```{r extract_variable_names}

file_list <- list.files(path = "D:/nldas", pattern = "^.*\\.(nc4|NC4|Nc4|Nc4)$",
                        full.names = FALSE) %>% 
  as_tibble() %>% 
  mutate(date = value %>% 
           stringr::str_extract("[1-2][0-9]{7}") %>% lubridate::ymd(),
         hour = value %>% 
           stringr::str_extract("[0-2][0-9][0]{2}") %>% as_factor(),
         path = paste0("D:/nldas/", value)) %>% 
  dplyr::select(value, path, date, hour) %>% 
  filter(date >= "1990-01-01")

# Designate file name list by start position

file_names <-
  file_list$value %>%
  as_tibble() %>% 
  dplyr::slice(., 10:n()) %>% 
  as_vector()


# Generate file list of missing files

saved_list <- list.files(path = "C:/Users/slewa/Documents/data/heat/nldas_raster/", pattern = "^.*\\.(rds)$",
                        full.names = FALSE) %>% 
  str_sub(end = -5L) %>% as_tibble()

file_names <-
  file_list %>% 
    mutate(day_hour = 
    paste0(
      file_list$value %>%  stringr::str_extract("[1-2][0-9]{7}"),
      "_",
      file_list$value %>% stringr::str_extract("\\.[0-2][0-9][0]{2}") %>% str_sub(start = 2L))) %>% 
    anti_join(., saved_list, by = c("day_hour" = "value")) %>% 
  dplyr::select(value) %>% 
  as_vector()


# Select from "file_names"
file_names <- file_names %>%
  as_tibble() %>% 
  dplyr::slice(., 41:n()) %>% 
  as_vector()





nldas_variables <- c("TMP", "SPFH", "PRES", "UGRD", "VGRD", "DSWRF")

```

## Raster: Read ncdf4 files

```{r id_raster_cells}
coordinates_matrix <- st_coordinates(army_select$centroid)

# file_split <- split(file_list$path, ceiling(seq_along(file_list$path)/100))

# file_list_small <- file_list$value[1:20]

#r <- raster(file_list$path[1], varname = "TMP", quick = "TRUE")

#cell <- tabularaster::cellnumbers(r, coordinates_matrix)
#rm(r)

#file_time <-
#  paste0(
#    file_list$path %>%  stringr::str_extract("[1-2][0-9]{7}"),
#    "_",
#    file_list$path %>% stringr::str_extract("[0-2][0-9][0]{2}"))
```


```{r extract_function}


cells <- readRDS("D:/nldas/cells.rds")
nldas_path <- "D:/nldas/"
# sites <- army_select$site_name
# cell_key <- cbind(sites, cells)
# output_path <- "D:/nldas/nldas_raster/"

# return single variable matrix column with date_hour as column name
  file_names_by_year$year1990$value[1] %>% 
    file.path(nldas_path, .) %>% 
      raster::brick(varname = "TMP", quick = TRUE) %>%
      raster::extract(., cells, df = FALSE) %>% 
      magrittr::set_colnames(paste0(
      file_names_by_year$year1990$value[1] %>%  stringr::str_extract("[1-2][0-9]{7}"),
      "_",
      file_names_by_year$year1990$value[1] %>% stringr::str_extract("[0-2][0-9][0]{2}")))
  

```

```{r extract_function_map}

# multiple variables

  
extract_single_file <- function(ncdf_single_file, nldas_var) {  
  hourly_df <-   
  ncdf_single_file %>% 
      file.path(nldas_path, .) %>% 
        raster::brick(varname = nldas_var, quick = TRUE) %>%
        raster::extract(., cells, df = FALSE) %>% 
        magrittr::set_colnames(nldas_var) %>%
    as_tibble()
}

extract_single_file <- compiler::cmpfun(extract_single_file)



 


# Execute map over files

ptm <- proc.time()

for (i in seq_along(file_names)) {
map2_dfc(.x = file_names[[i]], .y = nldas_variables, .f = extract_single_file) %>% 
write_rds(., path = paste0("C:/Users/slewa/Documents/data/heat/nldas_raster/",
                           paste0(
    file_names[[i]] %>%  stringr::str_extract("[1-2][0-9]{7}"),
    "_",
    file_names[[i]] %>% stringr::str_extract("\\.[0-2][0-9][0]{2}") %>% str_sub(start = 2L)),
    ".rds"), 
    compress = "none")
}

proc.time() - ptm



# single instance test
map2_dfc(.x = file_names[[1]], .y = nldas_variables, .f = extract_single_file) %>% 
write_rds(., path = paste0("D:/nldas_raster/",
                           paste0(
    file_names[[1]] %>%  stringr::str_extract("[1-2][0-9]{7}"),
    "_",
    file_names[[1]] %>% stringr::str_extract("\\.[0-2][0-9][0]{2}") %>% str_sub(start = 2L)),
    ".rds"), 
    compress = "none")

read_rds("D:/nldas_raster/19900101_0000.rds") %>% class()


ncdump::NetCDF("D:/nldas/NLDAS_FORA0125_H.A20090510.2000.002.grb.SUB.nc4")
```

corrupt files: 20090509_0500 to 20090510_2000 (41 files)

```{r}
raster_list <- list.files(path = "D:/nldas_raster",pattern = ".rds") %>%
  map(read_rds)
```



```{r long_exract_function}

  
################################################################3  
extract_variables_from_ncdf_file <- function(ncdf_filename_input) {
  cbind(
    ncdf_filename_input %>% 
      file.path(nldas_path, .) %>% 
        raster::brick(varname = nldas_variables[1], quick = TRUE) %>%
        raster::extract(., cells, df = FALSE) %>% 
        magrittr::set_colnames(nldas_variables[1]),
    
    ncdf_filename_input %>% 
      file.path(nldas_path, .) %>% 
        raster::brick(varname = nldas_variables[2], quick = TRUE) %>%
        raster::extract(., cells, df = FALSE) %>% 
        magrittr::set_colnames(nldas_variables[2]),
    
    ncdf_filename_input %>% 
      file.path(nldas_path, .) %>% 
        raster::brick(varname = nldas_variables[3], quick = TRUE) %>%
        raster::extract(., cells, df = FALSE) %>% 
        magrittr::set_colnames(nldas_variables[3]),
    
    ncdf_filename_input %>% 
      file.path(nldas_path, .) %>% 
        raster::brick(varname = nldas_variables[4], quick = TRUE) %>%
        raster::extract(., cells, df = FALSE) %>% 
        magrittr::set_colnames(nldas_variables[4]),
    
    ncdf_filename_input %>% 
      file.path(nldas_path, .) %>% 
        raster::brick(varname = nldas_variables[5], quick = TRUE) %>%
        raster::extract(., cells, df = FALSE) %>% 
        magrittr::set_colnames(nldas_variables[5]),
    
    ncdf_filename_input %>% 
      file.path(nldas_path, .) %>% 
        raster::brick(varname = nldas_variables[6], quick = TRUE) %>%
        raster::extract(., cells, df = FALSE) %>% 
        magrittr::set_colnames(nldas_variables[6])
  )
} 

# generate byte-compiled versions of functions
extract_variables_from_ncdf_file <- compiler::cmpfun(extract_variables_from_ncdf_file)
```



```{r split_nldas_file_list}
# split file list by year (from 1990 - 2019); ~8,760 hourly files per year



files_by_year <-
  file_list %>% 
    split(lubridate::year(.$date)) 

file_names_by_year <-
  lapply(files_by_year, `[`, 1)
names(file_names_by_year) <- paste0("year", names(file_names_by_year) )

files_by_yearmon <-
  file_list %>% 
    split(zoo::as.yearmon(.$date)) 
names(files_by_yearmon) <- janitor::make_clean_names(names(files_by_yearmon))


file_names_by_yearmon <-
  lapply(files_by_yearmon, `[`, 1) %>% 
  lapply(., as_vector)

file_names_by_yearmon[[1]][1] 

```




```{r plot_raster_cells}

centroid <- army_select$centroid %>%
  as_tibble() %>% 
  dplyr::mutate(site_name = army_select$site_name) %>% 
  st_as_sf()


raster_cell <- 
  xyFromCell(r, cell$cell_) %>%
  as_tibble() %>% 
  mutate(site_name = army_select$site_name) %>% 
  st_as_sf(coords = c("x", "y"))

raster_polygons <-
  xyFromCell(r, cell_polygons$cell_) %>%
  as_tibble() %>% 
  st_as_sf(coords = c("x", "y"))

tm_shape(army_select) +
    tm_borders() +
    tm_fill(col = "blue", alpha = 0.1) +
tm_shape(centroid) +
  tm_dots() +
tm_shape(raster_cell) +
  tm_dots(col = "red") +
tm_facets(by = "site_name")

```


