---
title: "read_nc4"
author: "SL"
date: "July 15, 2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(sf)
library(tidyverse)
library(viridis)
library(rvest)
library(rnaturalearth)
library(rnaturalearthdata)
library(rgeos)
library(lwgeom)
library(ncdf4)
library(devtools)
library(raster)
library(ncdump)
library(lubridate)
library(flipTime)
library(fuzzyjoin)
library(RNetCDF)
library(tidync)
library(furrr)
library(humidity)
library(HeatStress) #devtools::install_github("anacv/HeatStress")
library(weathermetrics)
library(wbgt)  #devtools::install_github("mdljts/wbgt")

```

```{r preliminary, echo = FALSE, include = FALSE}
## Preliminary (from `bases.Rmd`)

bases <- st_read("installations_ranges/MIRTA_Boundaries.shp") %>% 
  janitor::clean_names()

benning_geom <-
  bases %>%
    filter(stringr::str_detect(site_name, "Fort Benning")) %>% 
    dplyr::select(geometry) %>% st_union() 

## Create dataframe of active duty Army installations, including FSH (JBSA) and single Fort Benning row 
army_bases <-
  bases %>%
    filter(oper_stat == "Active") %>% 
    mutate(component = replace(component, site_name == "Fort Sam Houston", "Army Active")) %>%
    filter(component == "Army Active") %>%
    filter(site_name != "Fort Benning") %>%
    mutate(geometry = replace(geometry, site_name == "Fort Benning GA", benning_geom ))
   
## Filter installations of interest
army_select <-
  army_bases %>% 
    dplyr::filter(.$site_name %in% c("Fort Benning GA", "Fort Bragg","Fort Campbell",
                              "Fort Jackson", "Fort Polk", "Fort Hood",
                              "Fort Stewart", "Fort Leonard Wood", "Fort Riley",
                              "NTC and Fort Irwin")) %>% 
    mutate(centroid = st_centroid(geometry)) %>% 
    dplyr::select(-c("component", "joint_base", "country", "oper_stat"))


nldas_grid <- st_read("nldas_grids/NLDAS_Grid_Reference.shp") %>% 
  janitor::clean_names()

# Identify all NLDAS grids intersected by installation shapefiles
bases_nldas = NULL
for (i in 1:nrow(army_select)) {
  base = army_select[i,] 
  base_nldas = st_intersection(base, nldas_grid) 
  bases_nldas = rbind(bases_nldas, base_nldas)
}
rm(base, base_nldas)

# Calculate area of installation in each NLDAS grid and weight for spatial weighted average
nldas_weights <- bases_nldas %>% 
    mutate(area = sf::st_area(.$geometry)) %>% 
  group_by(site_name) %>% 
    mutate(sum_area = sum(area),
           weight = (area / sum_area)) %>% 
    dplyr::select(-c(nldas_x, nldas_y, area, centroid, sum_area))

# NLDAS grids that intersect with bases (to map full grid squares)
intersects = NULL
for (i in 1:nrow(army_select)) {
  base = army_select[i,] 
  base_intersect = nldas_grid %>% filter(lengths(st_intersects(., base)) > 0)
  intersects = rbind(intersects, base_intersect)
}
rm(base, base_intersect)

# Join `site_name` to selected NLDAS grid geometries
intersects <- intersects %>% left_join(dplyr::select(as_tibble(nldas_weights), c(nldas_id, site_name)), by = "nldas_id")

```



## Open 1st NetCDF file to inspect variable names
```{r extract_variable_names}

file_list <- list.files(path = "C:/Users/slewa/Documents/data/heat/nldas", pattern = "^.*\\.(nc4|NC4|Nc4|Nc4)$")


file_list <- paste0("C:/Users/slewa/Documents/data/heat/nldas/", file_list[1:3])
file_name <- file_list[1]

# Open a connection to the first file in  list
nc1 <- ncdf4::nc_open(file_name)

var_names <- attributes(nc1$var)$names
long_names <- vector("character", length = 11)
  
for (i in 1:11) {
   long_names[[i]] <- ncatt_get(nc1, attributes(nc1$var)$names[[i]])$long_name
}
long_names


# Close the connection to the nc file
nc_close(nc1)
```

```{r create_varlist, eval = FALSE, include = FALSE}
short_names <- c("evap", "longwave", "shortwave", "cape", "con_frac", "precip", "sp_humid", "merid_wind", "zonal_wind", "temperature", "pressure")

variables <- as_tibble(cbind(var_names, long_names, short_names))

var_list <- list(
  var_row = 1:nrow(variables),          
  var_name = variables$short_names
)
```



```{r process_single_ncdf, eval = FALSE, include = FALSE}

tidync("C:/Users/slewa/Documents/data/heat/nldas/NLDAS_FORA0125_H.A20000101.0000.002.grb.SUB.nc4") %>% activate(grid_identifier) %>% hyper_tibble()

nc_test <-
  tidync("C:/Users/slewa/Documents/data/heat/nldas/NLDAS_FORA0125_H.A20000101.0000.002.grb.SUB.nc4") %>%    
    hyper_filter(
      lat = between(lat, 35.04, 35.27 ),
      lon = between(lon, -79.38, -78.90)) 

hyper_vars(nc_test)
hyper_dims(nc_test)
hyper_grids(nc_test)


a <-
nc_test %>% 
  activate("D0,D1,D2,D5") %>% 
  hyper_tibble() %>% 
  dplyr::select(lon, lat, TMP, SPFH)

b <-
nc_test %>% 
  activate("D0,D1,D3,D5") %>% 
  hyper_tibble() %>% 
  dplyr::select(-height_2, -time)

c <- 
nc_test %>% 
  activate("D0,D1,D5") %>% 
  hyper_tibble() %>% 
  dplyr::select(-DLWRF, -CONVfrac, -PEVAP, -APCP, -time)

df1 <-
left_join(a, b, by = c("lat", "lon")) %>% 
    left_join(., c, by = c("lat", "lon")) %>% 
      mutate(date_time = 
               file_name %>% 
                stringr::str_extract("[1-2][0-9]{7}\\.[0-9]{2}[0]{2}") %>% 
                    flipTime::AsDateTime(., us.format = TRUE, time.zone = "UTC")) %>% 
      janitor::clean_names() 

df2 <-
df1 %>% 
        mutate(wind = sqrt(ugrd^2 + vgrd^2),
               rh = humidity::SH2RH(q = spfh, t = tmp, p = pres, isK = TRUE),
               tmp_c = weathermetrics::convert_temperature(tmp, old_metric = "kelvin", new_metric = "celsius"),
               dewp = weathermetrics::humidity.to.dewpoint(rh = rh, t = tmp_c, temperature.metric = "celsius"),
               heat_index_c = weather)

wbgt.Liljegren(df2$tas, df2$dewp, df2$wind, df2$radiation, df2$Dates, df2$lon, df2$lat)

length(df2$tmp_c)

class(df2)
wbgt.outdoors <- wbgt.Liljegren(tas=data_obs$tasmean, dewp=data_obs$dewp, wind=data_obs$wind, radiation=data_obs$solar, dates= data_obs$Dates, lon=-5.66, lat=40.96)

```


## Function to read ncdf4 files
- Filter by spatial bounding box coordinates
- Extract desired variables from grid/dimension and combine in dataframe

```{r read_ncdf_function}

read_nc4 <- function(input_file) {
  
  nc4 <- tidync(input_file) %>%    
    hyper_filter(
      lat = between(lat, 35.04, 35.27 ),
      lon = between(lon, -79.38, -78.90)) 
  
    a <-
      nc4 %>% 
        activate("D0,D1,D2,D5") %>% 
        hyper_tibble() %>% 
        dplyr::select(lon, lat, TMP, SPFH)

    b <-
      nc4 %>% 
        activate("D0,D1,D3,D5") %>% 
        hyper_tibble() %>% 
        dplyr::select(-height_2, -time)

    c <- 
      nc4 %>% 
        activate("D0,D1,D5") %>% 
        hyper_tibble() %>% 
        dplyr::select(-DLWRF, -CONVfrac, -PEVAP, -APCP, -time)

    left_join(a, b, by = c("lat", "lon")) %>% 
    left_join(., c, by = c("lat", "lon")) %>% 
    mutate(date_time = 
           file_name %>% 
                stringr::str_extract("[1-2][0-9]{7}\\.[0-9]{2}[0]{2}") %>%
                stringr::str_replace("(\\d{4})(\\d{2})(\\d{2})(\\.)(\\d{2})(\\d{2})$", "\\1-\\2-\\3 \\5:\\6\\:00") %>% 
                  flipTime::AsDateTime(us.format = TRUE, time.zone = "UTC")) %>% 
    janitor::clean_names() 

}

```

## Map over function with each ncdf4 file

```{r map_over_ncdf_function}

plan(multiprocess)

ptm <- proc.time()
nldas_df <- furrr::future_map_dfr(file_list, read_nc4, .progress = TRUE) 
proc.time() - ptm

nldas_df

```


## Join NLDAS grid ID and weight to dataframe

Fuzzy join used due to rounding differences at the fourth decimal place between NLDAS grid file centers and NetCDF download coordinates (all distances less than 0.00051 degrees). 

```{r join_gridid_weight}

nldas_df_weighted <-
  nldas_df %>%
    fuzzyjoin::difference_left_join(nldas_weights, by = c("lon" = "centerx", "lat" = "centery"), max_dist = 0.001, distance_col = "distance") %>% 
    dplyr::select(-c(centerx, centery, lat.distance, lon.distance)) %>%
    filter(!is.na(nldas_id)) 

nldas_df_weighted
```





```{r date_time, include = FALSE, eval = FALSE}


## Date/Time and WBGT code

time = as.POSIXct((strptime(paste(day, month, year, hour, sep = " "), "%d %m %Y %H%M"))))

mutate(date_time = 
               file_name %>% 
                stringr::str_extract("[1-2][0-9]{7}\\.[0-9]{2}[0]{2}"),
             year = stringr::str_sub(date_time, start = 1, end = 4),
             month = stringr::str_sub(date_time, start = 5, end = 6),
             day = stringr::str_sub(date_time, start = 7, end = 8),
             hour = stringr::str_sub(date_time, start = 10, end = 11),
             date = paste(year, month, day, sep = "-"),
             time = paste0(str_sub(hour, start = 1, end = 2), ":", "00", ":", "00"), 
             dates =  paste(date, time, sep = " ")) %>%   
             

## Mutate variables: wind speed, rh, temp(deg C), heat index)

      mutate(wind = sqrt(ugrd^2 + vgrd^2),
             rh = humidity::SH2RH(q = spfh, t = tmp, p = pres, isK = TRUE),
             tmp_c = weathermetrics::convert_temperature(tmp, old_metric = "kelvin", new_metric = "celsius"),
             dewp = weathermetrics::humidity.to.dewpoint(rh = rh, t = tmp_c, temperature.metric = "celsius"),
             heat_index_c = weathermetrics::heat.index(t = tmp_c, rh = rh, temperature.metric = "celsius", output.metric = "celsius", round = 2))


## WBGT Code

wbgt <-  HeatStress::wbgt.Liljegren(tas = df1$tmp_c, dewp = df1$dewp, wind = df1$wind, radiation = df1$dswrf, dates = df1$date_time, lon = df1$lon, lat = df1$lat)


HeatStress::wbgt.Liljegren(tas = 12.9, dewp = 4.96, wind = 1.24, radiation = 0, dates = "2000-01-01 00:00:00", lon = -79.3, lat = 35.1, tolerance = 1e-04, noNAs = TRUE, swap = FALSE, hour = TRUE)

load(file = "data_obs.rda")
data("data_obs") 
wbgt.outdoors <- wbgt.Liljegren(tas=data_obs$tasmean, dewp=data_obs$dewp, 
wind=data_obs$wind, radiation=data_obs$solar, dates= data_obs$Dates, lon=-5.66, lat=40.96)

load(file = "data_wbgt.Liljegren.rda")
data("data_wbgt.Liljegren") 

wbgt.outdoors[[1]]
data_wbgt.Liljegren[[1]]

```
