---
title: "workflow"
author: "SL"
date: "July 15, 2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(sf)
library(tidyverse)
library(viridis)
library(rvest)
library(rnaturalearth)
library(rnaturalearthdata)
library(rgeos)
library(lwgeom)
library(ncdf4)
library(devtools)
library(raster)
library(ncdump)
library(lubridate)
library(flipTime)
library(fuzzyjoin)
library(RNetCDF)
library(tidync)
library(furrr)
library(humidity)
library(HeatStress) #devtools::install_github("anacv/HeatStress")
library(weathermetrics)
library(wbgt)  #devtools::install_github("mdljts/wbgt")

```

```{r}

bases <- st_read("installations_ranges/MIRTA_Boundaries.shp") %>% 
  janitor::clean_names()

army_select <-
bases %>% 
  filter(.$site_name %in% c("Fort Bragg", "Fort Benning GA", "Fort Benning", "Fort Campbell" ))

bragg <-
bases %>% 
  filter(.$site_name == "Fort Bragg")

bb_bragg <-
st_bbox(bragg) %>% 
  .[c("ymin", "xmin", "ymax", "xmax")]

bb_bragg

bragg_centroid <- st_centroid(bragg)

```

```{r}
nldas_grid <- st_read("nldas_grids/NLDAS_Grid_Reference.shp") %>% 
  janitor::clean_names()

bragg_nldas <-
  st_intersection(bragg, nldas_grid) %>% 
  mutate(area = sf::st_area(.),
         weight = area / sum(area))

```

```{r}

file_list <- list.files(path = "C:/Users/slewa/Documents/data/heat/nldas", pattern = "^.*\\.(nc4|NC4|Nc4|Nc4)$")

file_list <- paste0("C:/Users/slewa/Documents/data/heat/nldas/", file_list[1:3])


# Open a connection to the first file in  list
nc1 <- ncdf4::nc_open(file_name)

var_names <- attributes(nc1$var)$names
long_names <- vector("character", length = 11)
  
for (i in 1:11) {
   long_names[[i]] <- ncatt_get(nc1, attributes(nc1$var)$names[[i]])$long_name
}
long_names

short_names <- c("evap", "longwave", "shortwave", "cape", "con_frac", "precip", "sp_humid", "merid_wind", "zonal_wind", "temperature", "pressure")

variables <- as_tibble(cbind(var_names, long_names, short_names))

var_list <- list(
  var_row = 1:nrow(variables),          
  var_name = variables$short_names
)

# Close the connection to the nc file
nc_close(nc1)
```

```{r}

tidync("C:/Users/slewa/Documents/data/heat/nldas/NLDAS_FORA0125_H.A20000101.0000.002.grb.SUB.nc4") %>% activate(grid_identifier) %>% hyper_tibble()

nc_test <-
  tidync("C:/Users/slewa/Documents/data/heat/nldas/NLDAS_FORA0125_H.A20000101.0000.002.grb.SUB.nc4") %>%    
    hyper_filter(
      lat = between(lat, 35.04, 35.27 ),
      lon = between(lon, -79.38, -78.90)) 

hyper_vars(nc_test)
hyper_dims(nc_test)
hyper_grids(nc_test)


a <-
nc_test %>% 
  activate("D0,D1,D2,D5") %>% 
  hyper_tibble() %>% 
  dplyr::select(lon, lat, TMP, SPFH)

b <-
nc_test %>% 
  activate("D0,D1,D3,D5") %>% 
  hyper_tibble() %>% 
  dplyr::select(-height_2, -time)

c <- 
nc_test %>% 
  activate("D0,D1,D5") %>% 
  hyper_tibble() %>% 
  dplyr::select(-DLWRF, -CONVfrac, -PEVAP, -APCP, -time)

df1 <-
left_join(a, b, by = c("lat", "lon")) %>% 
    left_join(., c, by = c("lat", "lon")) %>% 
      mutate(date_time = 
               file_name %>% 
                stringr::str_extract("[1-2][0-9]{7}\\.[0-9]{2}[0]{2}") %>% 
                    flipTime::AsDateTime(., us.format = TRUE, time.zone = "UTC")) %>% 
      janitor::clean_names() 

df2 <-
df1 %>% 
        mutate(wind = sqrt(ugrd^2 + vgrd^2),
               rh = humidity::SH2RH(q = spfh, t = tmp, p = pres, isK = TRUE),
               tmp_c = weathermetrics::convert_temperature(tmp, old_metric = "kelvin", new_metric = "celsius"),
               dewp = weathermetrics::humidity.to.dewpoint(rh = rh, t = tmp_c, temperature.metric = "celsius"),
               heat_index_c = weather)

wbgt.Liljegren(df2$tas, df2$dewp, df2$wind, df2$radiation, df2$Dates, df2$lon, df2$lat)

length(df2$tmp_c)

class(df2)
wbgt.outdoors <- wbgt.Liljegren(tas=data_obs$tasmean, dewp=data_obs$dewp, wind=data_obs$wind, radiation=data_obs$solar, dates= data_obs$Dates, lon=-5.66, lat=40.96)

```

## Date/Time code

time = as.POSIXct((strptime(paste(day, month, year, hour, sep = " "), "%d %m %Y %H%M"))))

mutate(date_time = 
               file_name %>% 
                stringr::str_extract("[1-2][0-9]{7}\\.[0-9]{2}[0]{2}"),
             year = stringr::str_sub(date_time, start = 1, end = 4),
             month = stringr::str_sub(date_time, start = 5, end = 6),
             day = stringr::str_sub(date_time, start = 7, end = 8),
             hour = stringr::str_sub(date_time, start = 10, end = 11),
             date = paste(year, month, day, sep = "-"),
             time = paste0(str_sub(hour, start = 1, end = 2), ":", "00", ":", "00"), 
             dates =  paste(date, time, sep = " ")) %>%   
             
## Mutate variables: wind speed, rh, temp(deg C), heat index)

      mutate(wind = sqrt(ugrd^2 + vgrd^2),
             rh = humidity::SH2RH(q = spfh, t = tmp, p = pres, isK = TRUE),
             tmp_c = weathermetrics::convert_temperature(tmp, old_metric = "kelvin", new_metric = "celsius"),
             dewp = weathermetrics::humidity.to.dewpoint(rh = rh, t = tmp_c, temperature.metric = "celsius"),
             heat_index_c = weathermetrics::heat.index(t = tmp_c, rh = rh, temperature.metric = "celsius", output.metric = "celsius", round = 2))


## WBGT Code
wbgt <-  HeatStress::wbgt.Liljegren(tas = df1$tmp_c, dewp = df1$dewp, wind = df1$wind, radiation = df1$dswrf, dates = df1$date_time, lon = df1$lon, lat = df1$lat)





             
HeatStress::wbgt.Liljegren(tas = 12.9, dewp = 4.96, wind = 1.24, radiation = 0, dates = "2000-01-01 00:00:00", lon = -79.3, lat = 35.1, tolerance = 1e-04, noNAs = TRUE, swap = FALSE, hour = TRUE)

load(file = "data_obs.rda")
data("data_obs") 
wbgt.outdoors <- wbgt.Liljegren(tas=data_obs$tasmean, dewp=data_obs$dewp, 
wind=data_obs$wind, radiation=data_obs$solar, dates= data_obs$Dates, lon=-5.66, lat=40.96)

load(file = "data_wbgt.Liljegren.rda")
data("data_wbgt.Liljegren") 

wbgt.outdoors[[1]]
data_wbgt.Liljegren[[1]]


```{r}


read_nc4 <- function(input_file) {
  
  nc4 <- tidync(input_file) %>%    
    hyper_filter(
      lat = between(lat, 35.04, 35.27 ),
      lon = between(lon, -79.38, -78.90)) 
  
    a <-
      nc4 %>% 
        activate("D0,D1,D2,D5") %>% 
        hyper_tibble() %>% 
        dplyr::select(lon, lat, TMP, SPFH)

    b <-
      nc4 %>% 
        activate("D0,D1,D3,D5") %>% 
        hyper_tibble() %>% 
        dplyr::select(-height_2, -time)

    c <- 
      nc4 %>% 
        activate("D0,D1,D5") %>% 
        hyper_tibble() %>% 
        dplyr::select(-DLWRF, -CONVfrac, -PEVAP, -APCP, -time)

    left_join(a, b, by = c("lat", "lon")) %>% 
    left_join(., c, by = c("lat", "lon")) %>% 
    mutate(date_time = 
           file_name %>% 
                stringr::str_extract("[1-2][0-9]{7}\\.[0-9]{2}[0]{2}") %>% 
                  flipTime::AsDateTime(.)) %>% 
    janitor::clean_names() %>% 
    mutate(wind = sqrt(ugrd^2 + vgrd^2),
           rh = humidity::SH2RH(spfh, tmp, pres),
           tmp_c = weathermetrics::convert_temperature(tmp, old_metric = "k", new_metric = "c"),
           dewp = weathermetrics::humidity.to.dewpoint(rh = rh, t = tmp_c, temperature.metric = "celsius"),
           wbgt = HeatStress::wbgt.Liljegren(tmp, dewp, wind, dswrf, date_time, lon, lat))

}





plan(multiprocess)

ptm <- proc.time()
df_out <- furrr::future_map_dfr(file_list, read_nc4, .progress = TRUE) 
proc.time() - ptm

df_out
```

